Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-28 WSSSPE2_report/WSSSPE2_review.tex
Section 10: Add a question in note.

The WSSSPE2 workshop continues our experiment from WSSSPE1 in how we can
collaboratively build a workshop agenda. The differences in WSSSPE2 from WSSSPE1
are in using an existing service (EasyChair) to handle submissions and reviews,
rather than an ad hoc process, and using an existing service (well-sorted) to
allow collaborative grouping of papers into themes by all authors, reviewers,
and the community, rather than this being done in an ad hoc manner by the
organizers alone.

>>>>

The WSSSPE2 workshop continues our experiment from WSSSPE1 in how we can
collaboratively build a workshop agenda. The differences in WSSSPE2 from WSSSPE1
are in using an existing service (EasyChair) to handle submissions and reviews,
rather than an ad hoc process, and using an existing service (well-sorted) to
allow collaborative grouping of papers into themes by all authors, reviewers,
and the community, rather than this being done in an ad hoc manner by the
organizers alone.\choinote{Are lightning talks new features in WSSSPE2?}
